### 2018-12-28 taco/tex/model.tex
Add taco

{\color{black}
\section{Framework Resources Quantification Model}\label{model}

\begin{figure*}
    \centering
	\includegraphics[width=0.85\textwidth]{fig/model_basic}
	\caption{\color{black}Framework Resources Quantification (FRQ) Model with Full Parallel MapReduce}
    \label{fig:model_basic}
    \vspace{-1em}
\end{figure*}

@@

@@

\begin{figure}
	\centering
	\begin{minipage}[hb]{\linewidth}
		\begin{subfigure}{\linewidth}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/model_original}
				\caption{\color{black}Full Serial MapReduce}
				\label{fig:model_original}
			\end{minipage}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/model_hadoop}
				\caption{\color{black}Half Parallel MapReduce}
				\label{fig:model_hadoop}
			\end{minipage}
		\end{subfigure}
		\caption{\color{black}Framework Resources Quantification (FRQ) Model with Different Scheduling Strategies}
		\label{fig:model_strategies}
	\end{minipage}
\end{figure}

@@

\begin{figure}
	\centering
	\begin{minipage}[hb]{\linewidth}
		\begin{subfigure}{\linewidth}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/model_scache1}
				\caption{\color{black}If \(V_{Map} \times R \ge V_{Shuffle}\)}
				\label{fig:model_scache1}
			\end{minipage}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/model_scache2}
				\caption{\color{black}If \(V_{Map} \times R < V_{Shuffle}\)}
				\label{fig:model_scache2}
			\end{minipage}
		\end{subfigure}
		\caption{\color{black}Framework Resources Quantification (FRQ) Model with Full Parallel MapReduce in Different Environments}
		\label{fig:model_scache}
	\end{minipage}
\end{figure}

@@

\begin{table*}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{\color{black}Hadoop MapReduce on 4 nodes cluster in the FRQ model}
\label{table1}
\centering
\(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
\hline
 &
\(D\) &	
\(R\) &	
\(N\) &	
\(V_{Map}\) &	
\(V_{Reduce}\) &	
\(V_{Shuffle}\) &	
\(K\) &	
\(T_{Map}\) &	
\(T_{Shuffle}\) &	
\(T_{P\_Shuffle}\) &
\(T_{Reduce}\) & 
\(T_{Job}\) & 
\(Exp T_{Job}\) &
\(Error\)\\

\hline
 & 16	& 1	& 2 &	0.65 &	1 &	0.47 &	0.5 &	24.62 &		34.04	 &	21.73 &	26.87 &	51.48	& 55  &		6.39\% \\
 SCache
 & 32	& 1	& 4 &	0.65 &	1 &	0.47 &	0.5 &	49.23 &		68.09	 &	31.16 &	47.58 &	96.81	& 104 & 	6.91\% \\
 & 48	& 1	& 6 &	0.65 &	1 &	0.47 &	0.5 &	73.85 &		102.13 &	40.59 &	68.29 &	142.14	& 151 & 	5.87\% \\
 & 64	& 1	& 8 &	0.65 &	1 &	0.47 &	0.5 &	98.46 &		136.17 &	50.02 &	89.01 &	187.47	& 193 & 	2.87\% \\
 \hline
 & 16	& 1 & 2 &	0.65 &	1 &	0.47 &	0.6 &	24.62 &		34.04	&	34.04	&	36.43	&	61.04	&	73	&	16.38\%	\\
 Legacy
 & 32	& 1 & 4 &	0.65 &	1 &	0.47 &	0.6 &	49.23 &		68.09	&	68.09	&	72.85	&	122.08	&	135	&	9.57\%	\\
 & 48	& 1 & 6 &	0.65 &	1 &	0.47 &	0.6 &	73.85 &		102.13	&	102.13	&	109.28	&	183.12	&	188	&	2.59\%	\\
 & 64	& 1 & 8 &	0.65 &	1 &	0.47 &	0.6 &	98.46 &		136.17	&	136.17	&	145.70	&	244.16	&	249	&	1.94\%	\\
\hline
\end{tabular}
\end{table*}
% \subsection{Performance Analysis}\label{model_performance_analysis}

\begin{table*}[!t]

\renewcommand{\arraystretch}{1.3}
\caption{\color{black}Hadoop MapReduce on 50 AWS m4.xlarge nodes cluster in the FRQ model}
\label{table2}
\centering
\(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
\hline
 &
\(D\) &	
\(R\) &	
\(N\) &	
\(V_{Map}\) &	
\(V_{Reduce}\) &	
\(V_{Shuffle}\) &	
\(K\) &	
\(T_{Map}\) &	
\(T_{Shuffle}\) &	
\(T_{P\_Shuffle}\) &
\(T_{Reduce}\) & 
\(T_{Job}\) & 
\(Exp T_{Job}\) &
\(Error\)\\

@@

\hline
\end{tabular}
\end{table*}

@@

\begin{figure}
	\centering
	\begin{minipage}[hb]{\linewidth}
		\begin{subfigure}{\linewidth}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/hadoop_net1}
				\caption{\color{black}If \(V_{Map} \times R \ge V_{Shuffle}\)}
				\label{fig:hadoop_net1}
			\end{minipage}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/hadoop_net2}
				\caption{\color{black}If \(V_{Map} \times R < V_{Shuffle}\)}
				\label{fig:hadoop_net2}
			\end{minipage}
		\end{subfigure}
		\caption{\color{black}Network utilization on Hadoop MapReduce with SCache}
		\label{fig:hadoop_net}
	\end{minipage}
\end{figure}

>>>>

{\color{blue}
\section{Framework Resources Quantification Model}\label{model}

@@

\begin{figure*}
    \centering
	\includegraphics[width=0.85\textwidth]{fig/model_basic}
	\caption{\color{blue}Framework Resources Quantification (FRQ) Model with Full Parallel MapReduce}
    \label{fig:model_basic}
    \vspace{-1em}
\end{figure*}

@@

\begin{figure}
	\centering
	\begin{subfigure}{0.47\linewidth}
		\includegraphics[width=\linewidth]{fig/model_original}
		\caption{\color{blue}Full Serial MapReduce}
		\label{fig:model_original}
	\end{subfigure}
	\begin{subfigure}{0.47\linewidth}
		\includegraphics[width=\linewidth]{fig/model_hadoop}
		\caption{\color{blue}Half Parallel MapReduce}
		\label{fig:model_hadoop}
	\end{subfigure}
	\caption{\color{blue}Framework Resources Quantification (FRQ) Model with Different Scheduling Strategies}
	\label{fig:model_strategies}
\end{figure}

@@

\begin{figure*}
	\centering
	\begin{subfigure}{0.47\linewidth}
		\includegraphics[width=\linewidth]{fig/model_scache1}
		\caption{\color{blue}If \(V_{Map} \times R \ge V_{Shuffle}\)}
		\label{fig:model_scache1}
	\end{subfigure}
	\begin{subfigure}{0.47\linewidth}
		\includegraphics[width=\linewidth]{fig/model_scache2}
		\caption{\color{blue}If \(V_{Map} \times R < V_{Shuffle}\)}
		\label{fig:model_scache2}
	\end{subfigure}
	\caption{\color{blue}Framework Resources Quantification (FRQ) Model with Full Parallel MapReduce in Different Environments}
	\label{fig:model_scache}
\end{figure*}

@@

\begin{table}[!t]
% \renewcommand{\arraystretch}{0.8}
\caption{\color{blue}Hadoop MapReduce on 4 nodes cluster in the FRQ model}
\label{table1}
\begin{minipage}{\columnwidth}
\centering
\(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
\scalebox{0.75}{
	\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
	\hline
	&
	\(D\) &	
	\(R\) &	
	\(N\) &	
	\(V_{Map}\) &	
	\(V_{Reduce}\) &	
	\(V_{Shuffle}\) &	
	\(K\) &	
	\(T_{Map}\) &	
	\(T_{Shuffle}\) &	
	\(T_{P\_Shuffle}\) &
	\(T_{Reduce}\) & 
	\(T_{Job}\) & 
	\(Exp T_{Job}\) &
	\(Error\)\\

	\hline
	& 16	& 1	& 2 &	0.65 &	1 &	0.47 &	0.5 &	24.62 &		34.04	 &	21.73 &	26.87 &	51.48	& 55  &		6.39\% \\
	SCache
	& 32	& 1	& 4 &	0.65 &	1 &	0.47 &	0.5 &	49.23 &		68.09	 &	31.16 &	47.58 &	96.81	& 104 & 	6.91\% \\
	& 48	& 1	& 6 &	0.65 &	1 &	0.47 &	0.5 &	73.85 &		102.13 &	40.59 &	68.29 &	142.14	& 151 & 	5.87\% \\
	& 64	& 1	& 8 &	0.65 &	1 &	0.47 &	0.5 &	98.46 &		136.17 &	50.02 &	89.01 &	187.47	& 193 & 	2.87\% \\
	\hline
	& 16	& 1 & 2 &	0.65 &	1 &	0.47 &	0.6 &	24.62 &		34.04	&	34.04	&	36.43	&	61.04	&	73	&	16.38\%	\\
	Legacy
	& 32	& 1 & 4 &	0.65 &	1 &	0.47 &	0.6 &	49.23 &		68.09	&	68.09	&	72.85	&	122.08	&	135	&	9.57\%	\\
	& 48	& 1 & 6 &	0.65 &	1 &	0.47 &	0.6 &	73.85 &		102.13	&	102.13	&	109.28	&	183.12	&	188	&	2.59\%	\\
	& 64	& 1 & 8 &	0.65 &	1 &	0.47 &	0.6 &	98.46 &		136.17	&	136.17	&	145.70	&	244.16	&	249	&	1.94\%	\\
	\hline
	\end{tabular}
}
\end{minipage}
\end{table}
% \subsection{Performance Analysis}\label{model_performance_analysis}

\begin{table*}[!t]
\caption{\color{blue}Hadoop MapReduce on 50 AWS m4.xlarge nodes cluster in the FRQ model}
\label{table2}
\centering
\(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
\scalebox{0.75}{
	\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
	\hline
	&
	\(D\) &	
	\(R\) &	
	\(N\) &	
	\(V_{Map}\) &	
	\(V_{Reduce}\) &	
	\(V_{Shuffle}\) &	
	\(K\) &	
	\(T_{Map}\) &	
	\(T_{Shuffle}\) &	
	\(T_{P\_Shuffle}\) &
	\(T_{Reduce}\) & 
	\(T_{Job}\) & 
	\(Exp T_{Job}\) &
	\(Error\)\\

@@

	\hline
	\end{tabular}
}
\end{table*}

@@

\begin{figure}
	\centering
	\begin{subfigure}{.47\linewidth}
		\includegraphics[width=\linewidth]{fig/hadoop_net1}
		\caption{\color{blue}If \(V_{Map} \times R \ge V_{Shuffle}\)}
		\label{fig:hadoop_net1}
	\end{subfigure}
	\begin{subfigure}{.47\linewidth}
		\includegraphics[width=\linewidth]{fig/hadoop_net2}
		\caption{\color{blue}If \(V_{Map} \times R < V_{Shuffle}\)}
		\label{fig:hadoop_net2}
	\end{subfigure}
	\caption{\color{blue}Network utilization on Hadoop MapReduce with SCache}
	\label{fig:hadoop_net}
\end{figure}
